Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-07 doc/Paper/main.tex
Replaced some plots and updated table.

    \begin{table*}
      \caption{Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits denote the values derived for our fiducial analysis. The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
\caption{Measured auto- and cross power spectra considered in our analysis. The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
\label{fig:cls-best-fit}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}} 
\caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.} 
\label{fig:hod-params-z-dep}
\end{center}
\end{figure}

@@

\begin{sidewaystable}
\caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{95.8}{80}$ $(0.11)$ & $2.93\substack{+1.56 \\ -1.47}$ & $12.29 \pm 0.15$ & $6.00\substack{+2.14 \\ -2.05}$ & $13.69 \pm 0.21$ & - & - & - \\
auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.32\substack{+2.03 \\ -1.79}$ & $12.32 \pm 0.14$ & $6.49\substack{+2.80 \\ -2.47}$ & $13.72\substack{+0.20 \\ -0.19}$  & - & - & - \\
G cov & $\sfrac{98.4}{80}$ $(0.080)$ & $3.59\substack{+1.52 \\ -1.44}$ & $12.34 \pm 0.14$ & $6.89\substack{+1.96 \\ -1.89}$ & $13.74\substack{+0.19 \\ -0.20}$ & - & - & - \\
G+SSC cov & $\sfrac{97.8}{80}$ $(0.086)$ & $3.28\substack{+1.57 \\ -1.51}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.46\substack{+2.15 \\ -2.10}$ & $13.71 \pm 0.20$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{97.8}{84}$ $(0.14)$ & $2.69\substack{+1.17 \\ -1.08}$ & $12.24 \pm 0.09$ & $5.74\substack{+1.95 \\ -1.66}$ & $13.62\substack{+0.14 \\ -0.13}$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{102.2}{88}$ $(0.18)$ & $3.23 \pm 0.76$ & $12.27 \pm 0.06$ & $6.43\substack{+1.17 \\ -1.18}$ & $13.65 \pm 0.10$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{56.2}{43}$ $(0.085)$ & $2.83\substack{+2.25 \\ -2.11}$ & $12.26\substack{+0.18 \\ -0.19}$ & $5.44\substack{+3.07 \\ -2.93}$ & $13.64\substack{+0.25 \\ -0.26}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{45.8}{46}$ $(0.48)$ & $2.38\substack{+2.32 \\ -2.26}$ & $12.16\substack{+0.25 \\ -0.13}$ & $5.31\substack{+3.17 \\ -3.09}$ & $13.53\substack{+0.32 \\ -0.19}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{99.8}{80}$ $(0.066)$ & $2.96\substack{+1.22 \\ -1.12}$ & $12.45 \pm 0.11$ & $6.07\substack{+1.66 \\ -1.54}$ & $13.90 \pm 0.16$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{107.6}{80}$ $(0.022)$ & $3.18\substack{+1.24 \\ -1.27}$ & $12.43 \pm 0.12$ & $6.34\substack{+1.75 \\ -1.77}$ & $13.87 \pm 0.17$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{106.4}{80}$ $(0.026)$ & $2.90\substack{+1.35 \\ -1.33}$ & $12.37 \pm 0.12$ & $5.95\substack{+1.87 \\ -1.83}$ & $13.78 \pm 0.17$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{98.6}{80}$ $(0.078)$ & $2.66\substack{+1.17 \\ -1.08}$ & $12.45 \pm 0.11$ & $5.63\substack{+1.61 \\ -1.51}$ & $13.88 \pm 0.16$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
\caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
\caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
\caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}} 
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}} 
\caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model. The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
\label{fig:HOD-redshift}
\end{center}
\end{figure}

@@

    \begin{figure}
      \begin{center}
        \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
        \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
      \end{center}
    \end{figure}

>>>>

    \begin{table*}
      \caption{\todo{UPDATE} Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits denote the values derived for our fiducial analysis. The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
\caption{\todo{UPDATE} Measured auto- and cross power spectra considered in our analysis. The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
\label{fig:cls-best-fit}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}} 
\caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.} 
\label{fig:hod-params-z-dep}
\end{center}
\end{figure}

@@

\begin{sidewaystable}
\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants. The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$. In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$. The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
\begin{center}
\begin{tabular}{ccccccccc}
\hline\hline 
Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
G cov & $\sfrac{84.0}{80}$ $(0.36)$ & $0.361\substack{+3.06 \\ -2.63}$ & $11.89\substack{+0.23 \\ -0.24}$ & $2.01\substack{+3.97 \\ -3.41}$ & $13.09\substack{+0.28 \\ -0.29}$ & - & - & - \\
G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
 \hline \hline
\end{tabular}
\end{center}
\end{sidewaystable}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
\caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
\caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
\caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
\label{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}} 
\caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model. The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
\label{fig:HOD-redshift}
\end{center}
\end{figure}

@@

    \begin{figure}
      \begin{center}
        \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
        \caption{\todo{UPDATE} Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
        \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
      \end{center}
    \end{figure}
